---
title: "Developing Data Products Week 4 Project"
author: "Dale Hurd"
date: "2022-09-28"
output: ioslides_presentation 


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## 
Developing Data Products Week 4 Project Pitch

### A review of PGA Tour  Player Statistics

- URL: *https://github.com/dalehurd/developing-data-products-Week-4-*
- Find here all the data that have been use for this presentation and also for the first part of the data Science Project: "First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Rstudio Presenter to prepare a reproducible pitch presentation about your application."

### Find all details here
- URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

## PGA Statistics Dataset{.smaller} 
```{r data, echo = TRUE, comment=""}
data <- read.csv("ASA All PGA Raw Data - Tourn Level.csv", colClasses = "character") 
head(data, n=1)
```
## PGA Statistics Dataset - Format

**A data frame with 3676 observations on 37 variables.**

**Our Shiny App will utilize the following 3 data fields**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 21] | player| Name |
| [, 31]  | Finish | Finish |
| [, 37]	| sg_total| Strokes Gained Total |


## Analysis - Main Code  

```r
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)  })
  ...
  output$fit <- renderPrint({
    summary(fit()) })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })  })
```

