---
title: "Developing Data Products Week 4 Project"
author: "Dale Hurd"
date: "2022-09-28"
output: ioslides_presentation 


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## 
Developing Data Products Week 4 Project Pitch

### A review of PGA Tour  Player Statistics

- URL: *https://github.com/dalehurd/developing-data-products-Week-4-*
- Find here all the data that have been use for this presentation and also for the first part of the data Science Project: "First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Rstudio Presenter to prepare a reproducible pitch presentation about your application."

### Find all details here
- URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

## PGA Statistics Dataset{.smaller} 
```{r data, echo = TRUE, comment=""}
data <- read.csv("ASA All PGA Raw Data - Tourn Level.csv", colClasses = "character") 
head(data, n=1)
```
## PGA Statistics Dataset - Format

**A data frame with 3676 observations on 37 variables.**

**Our Shiny App will utilize the following 3 data fields**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 21] | player| Name |
| [, 31]  | Finish | Finish |
| [, 37]	| sg_total| Strokes Gained Total |
**We will simply plot the sg_total (Strokes gained total) versus the Finish statistic for two selected players**

**This is easily extensible to other categorical analysis**

## Analysis - Main Code  

```r
 shinyServer(function(input, output) {
  output$plot1 <- renderPlot({

    pr1 <- datap[datap$player==input$variable1,]


    dataX1 <- pr1$Finish
    dataX1fixed <- gsub('T','',dataX1)
    dataY1 <- pr1$sg_total




        plot(dataX1fixed, dataY1
             , 
             xlab = "Finish", ylab = "SG Total", main = input$variable1,
             xlim = c(0,70), ylim = c(-5,5))

        })
```

